---
title: "Weight of Fish"
author: "Eden Williams"
date: "Summer 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish= read.csv("Fish.csv")
Perch = filter(Fish, Species == 'Perch')
Pike = filter(Fish, Species=="Pike")
Roach= filter(Fish, Species == "Roach")
```

# Predicting Fish Weight

```{r}
pwt = lm(Perch$Weight~ Perch$Length1+Length2+Length3+Height, data= Perch)
summary(pwt)
```


## Perch
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```


```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```


### Best Models
The two best single variables to predict weight for Perch are Length3 and Height.

### Best Two regressor model

The best two regressor model for Perch would be Lenght3 and Height.

## Pike

```{r}
pwt = lm(Pike$Weight~ Pike$Length1+Length2+Length3+Height, data= Pike)
summary(pwt)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```


### Best Models

The two best single variables for predicting weight for Pike are Length2 and Length3.


### Best Two regressor model


The best two regressor model for Pike would be Length1 and Length3.



## Roach

```{r}
pwt = lm(Roach$Weight~ Roach$Length1+Length2+Length3+Height, data= Roach)
summary(pwt)
```



```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```




### Best Models

The two best variables for predicting weight for Roach are Length3 and Length2.

### Best Two regressor model

The best two regressor model for Roach would be Length1 and Length3.

## Final Summary Statements
Based upon the graphs above we can see which variables are the best predictors for determining the weight of the different groups of fish. 